---
title: "Linear Models"
author: "Eric Morris"
date: "11/8/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)

set.seed(1)

```

## Model Fitting 

Looking at airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group,
         neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Fit a model for price as an outcome

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
```

Look at some summaries (this is long and ugly and why we will be using the broom package: 

```{r}
summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
```

Better summaries using broom

```{r}
broom::tidy(fit)

fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "^boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
```

Look at other summaries

```{r}
fit %>% 
  broom::glance() %>% 
  select(r.squared, adj.r.squared)
```

Be careful with factors...(we were comparing to bronx). Just changing reference group to Manhattan in our model 

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(boro = fct_infreq(boro),
         room_type = fct_infreq(room_type))

fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>% 
  broom::tidy()
```


## Diagnostics 

modelr package can be used to add residuals

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) + geom_boxplot()

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point()

modelr::add_predictions(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = pred, color = boro)) + geom_point()
```

## Hypothesis Testing

Compare nested models

```{r}
fit_null = lm(price ~ stars + boro, data = nyc_airbnb)

fit_alt = lm(price ~ stars + boro + room_type, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

##Nested data

```{r}
nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Nesting and then fitting model

```{r}
nest_lm_res =
  nyc_airbnb %>% 
  group_by(boro) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest()
```

```{r}
nest_lm_res %>% 
  select(boro, term, estimate) %>% 
  mutate(term = fct_inorder(term)) %>% 
  spread(key = term, value = estimate) %>% 
  knitr::kable(digits = 3)
```

Xtreme

```{r}
manhattan_airbnb =
  nyc_airbnb %>% 
  filter(boro == "Manhattan")

manhattan_nest_lm_res =
  manhattan_airbnb %>% 
  group_by(neighborhood) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest()
```

Viewing results 

```{r}
manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + geom_point() + facet_grid(~term) + theme(axis.text.x = element_text(angle = 80, hjust = 1))
```


## Binary outcome in glm

```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") %>% 
  filter(city == "Baltimore") %>% 
  mutate(resolved = as.numeric(disposition == "Closed by arrest"),
         victim_age = as.numeric(victim_age),
         victim_race = fct_relevel(victim_race, "White")) %>% 
  select(resolved, victim_age, victim_race, victim_sex)
```

```{r}
fit_logistic = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)
```

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = boot::inv.logit(estimate)) %>% 
  knitr::kable(digits = 3)
```

```{r}
baltimore_df %>% 
  ggplot(aes(x = victim_age, y = resolved)) + geom_point()+ geom_smooth()
```

